%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Results and Verification with Measured Data}
\label{sec:comp_results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
The objective of this paper is to demonstrate the capability of detached eddy
simulations to predict aerodynamic loads on a static cylinder and an
elastically-mounted cylinder.  Verification with existing experimental data in
the literature, and data from new experiments conducted as a part of this
study, are presented for both the static cylinder and the elastically-mounted
cylinder. Smooth inflow is used -- zero turbulence in the numerical simulations
and the minimum possible inflow turbulence intensity ($\sim$0.2\%) in the
tunnel. Cylinder surface is very smooth and hence surface roughness is not
modeled in the simulations.

Static testing is performed for (1) flow normal to the cylinder axis, and (2)
flow at an angle to the cylinder axis (inclined cylinder); three inclination
angles are analyzed in this study. These cases are simulated at Reynolds number
$Re_D=20,000$ which is corresponding to laminar separation (LS), where flows
are laminar before separation and transition to turbulence occurs in the shear
layer.

Dynamic testing is performed for an elastically-mounted cylinder in eight
different inflow reduce velocities with (1) flow normal to the cylinder axis,
and (2) flow at an angle to the cylinder axis (inclined cylinder). However, due
to high computational cost of simulations, only one inclination angle is
analyzed in the dynamic study($45^\circ$). The cylinder is limited to vibrate
along the direction which is perpendicular to both the flow direction and the
cylinder axis. All dynamic cases are simulated at the same Reynolds number,
$Re_{D,n}=20,000$.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% input section
\input{staticResults.tex}

% input section
\input{viv.tex}
